\newpage
\section{User Stories}

\begin{itemize}
	\item Overview on login
	\begin{itemize}
		\item As a user, I would like to see an overview of my profile after logging in.
	\end{itemize}

	\item Viewing Borrowers
	\begin{itemize}
		\item As a lender I would like to be able to search through all borrowers currently asking for a loan, as a list with optional filters.
	\end{itemize}

	\item My loan overview
	\begin{itemize}
		\item As a lender I would like to view my current loan plans with information about the total amount lended, amount given back, and estimate for completion.
	\end{itemize}

	\item Loan Custom Plans
	\begin{itemize}
		\item As a lender I would like the ability to create a loan proposal for a borrower with custom inception triggers.
	\end{itemize}

	\item Partial Loans
	\begin{itemize}
		\item As a lender I would like to be able to give a partial loan to a borrower.
	\end{itemize}

	\item Borrower information
	\begin{itemize}
		\item As a lender I would like to be able to view borrowers documents, such as resumes and portfolios.
	\end{itemize}

	\item Risk Evaluation
	\begin{itemize}
		\item As a lender I would like to see a borrowers evaluated risk, as well as the information used to calculate the risk.
	\end{itemize}

	\item Bank Connection
	\begin{itemize}
		\item As a lender I would like Mutuari to be able to deposit dircetly to my bank account, and withdraw with explicit confirmations.
	\end{itemize}

	\item Complete Statement
	\begin{itemize}
		\item As a user I would like to get a printable document of all my previous and current interactions.
		\item This document should have transaction amounts, the user that was transacted with, and information about when loans were started and completed.
	\end{itemize}

	\item Bank Account Customization
	\begin{itemize}
		\item As a lender I would like the ability to set up deposits to one bank account and withrawals from a different account.
	\end{itemize}

	\item Create Account
	\begin{itemize}
		\item As a new user, after clicking sign up, a modal should appear with fields to be completed to check if the potential user qualifies to use our services.
	\end{itemize}

	\item Borrower creates a profile
	\begin{itemize}
		\item As a borrower I would like to create my profile after signing up for service.
		\item This profile is different from the Lender profile.
	\end{itemize}

	\item Delete Borrower profile
	\begin{itemize}
		\item If I do not owe any money on loans, I should be able to delete my borrower profile/cancel the service.
	\end{itemize}

	\item Editing Borrower profile
	\begin{itemize}
		\item After creating a profile, a borrower should be able to edit the profile page and have changes displayed.
	\end{itemize}

	\item Lender creates a profile
	\begin{itemize}
		\item As a Lender I would like to create my profile after signing up for service.
		\item This profile is different from the Borrower profile.
	\end{itemize}

	\item Delete Lender Account
	\begin{itemize}
		\item As a lender, if I have no active loans, I should be able to cancel/remove my account from the platform.
	\end{itemize}

	\item Boilerplate loans
	\begin{itemize}
		\item The platform should have a few boilerplate loan plans for lenders that do not wish to create their own custom plans.
	\end{itemize}

	\item Contact support
	\begin{itemize}
		\item There should be a way for both types of users to contact Mutuari for support.
	\end{itemize}

	\item Supporting documents
	\begin{itemize}
		\item As a user I should have access to some sort of documentation that explains how the service works.
	\end{itemize}

\end{itemize}
